Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-17 paper/sections/conclusions.tex
[ paper ] minor changes.

We presented a reliable proof-reconstruction in type theory of \Metis
solutions for problems in classical propositional logic without
equality. As a product of this research, we built a proof-reconstruction tool written in \Haskell. This tool generates
\Agda proof-terms of \Metis \TSTP derivations. \Agda files
delivered by the aforementioned tool are supported by the
formalization in \Agda of the \Metis rules described in
Section~\ref{ssec:emulating-inferences}.

@@

One of the main contribution of this study was
increasing the trustworthiness of the automatic provers,
in our case, \Metis.
Justifying a proof-object of a theorem prover
has a real significant impact for these automatic tools.
The reverse engineering task can reveal important issues or bugs
in many parts of these system (e.g., preprocessing, reasoning, or
deduction modules). During this research, we had the opportunity
to find some of bugs\footnote{Issues No.~2, No.~4. and
commit \name{8a3f11e} in the \Metis' official repository
\url{https://github.com/gilith/metis}} in \Metis.
Fortunately, all these problems were fixed quickly by Joe Hurd in
20170810 release.

>>>>

We presented a reliable proof-reconstruction in type theory of \Metis
solutions for problems in classical propositional logic without
equality. As a product of this research, we built a proof-reconstruction tool written in \Haskell. This tool generates
\Agda proof-terms of \Metis \TSTP derivations. \Agda files
delivered by the aforementioned tool are supported by the
formalization in \Agda~\cite{AgdaProp,AgdaMetis} of the \Metis rules
described in Section~\ref{ssec:emulating-inferences}.

@@

One of the main contribution of this study was
increasing the trustworthiness of the automatic provers,
in our case, \Metis.
Justifying a proof-object of a theorem prover
has a real significant impact for these automatic tools.
The reverse engineering task can reveal important issues or bugs
in many parts of these system (e.g., preprocessing, reasoning, or
deduction modules). During this research, we had the opportunity
to improve \Metis by reporting some bugs\footnote{Issues No.~2,
No.~4. and commit \name{8a3f11e} in the \Metis' official repository
\url{https://github.com/gilith/metis}} in \Metis.
Fortunately, all these problems were fixed quickly by Joe Hurd in
20170810 release.

### 2017-10-17 paper/sections/related-work.tex
[ paper ] minor changes.

Kanso and Setzer~\cite{kanso2016light} integrate the propositional fragment of \name{EProver} in \Agda. In this work, the authors translate automatically propositional logic problems written in \Agda to \TPTP problems. By calling an external wrapper of the ATP, this tool gets a \TSTP derivation. The tool parses the \name{EProver} derivation and outputs
\Agda code. After that, we say their proof-reconstruction is almost
similar as the approach presented in Section~\ref{ssec:workflow}.
Nevertheless, Kanso and Setzer aim to justify some of the inference rules
by using propositional semantics instead of a only syntactic treatment. We showed here a kind of treatment to justify \Metis proof-objects.
\end{document}

>>>>

Kanso and Setzer~\cite{kanso2016light} integrate the propositional
fragment of \name{EProver} in \Agda. In this work, the authors
translate automatically propositional logic problems written in \Agda
to \TPTP problems. By calling an external wrapper of the ATP, this
tool gets a \TSTP derivation. The tool parses the \name{EProver}
derivation and outputs \Agda code.
We able to say their proof-reconstruction is almost
similar as the approach presented in Section~\ref{ssec:workflow}.
Nevertheless, Kanso and Setzer aim to justify some of the inference
rules by using propositional semantics instead of an only syntactic
treatment as we did in this work.

\end{document}
